### 2021-07-06 paper/paper.tex
through 3.3.1

While you may already know how to use test case generation from the snippet in the introduction, it can help to think of automated test case generation as a set of steps, each of which has choices to make.
\begin{enumerate}
   \item Identify the system under test. It may be a function, but it could correspond to an \textsc{api} or an application.
   \item Decide how a single test case, consisting of argument values, should correspond to a unit test.
   \item Address the risk associated with different arguments.
   \item Pick a test generation strategy.
   \item Choose a method for checking the results of each test.
\end{enumerate}
We'll explore these steps in this section.

@@

We have assumed, thus far, that we are unit testing a function. In that case, the function has arguments and those arguments can take on particular values. Our test cases will correspond exactly to an invocation of the function. However, this need not be the case. The tool can be used more generally. Combinatorial testing is used outside Julia. It would apply, for instance, to testing compatibility of hardware subsystems.

A common case in Julia is testing a scientific application at the user level. Here, we can consider the user's choices of command-line arguments and parameters in files. We could even generate classes of data according to keys that we assign to arguments in \utd.

@@

Some arguments to a function can take on only a few allowed values, such as \verb|true| or \verb|false|, but most arguments are integers, floating-point, or more complicated data structures. The theory of covering arrays presumes any argument will be assigned only one of a few values, so we need to make choices.

\vskip 6pt
We're looking for faults in the code that lead to failures of unit tests. These faults will be visible, or invisible, for different choices of argument values. If a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults. Our goal, as authors of unit tests, is to select argument values that represent equivalence classes for the function under test. There isn't a lot of guidance on how to choose these values. You can guess them by looking at the code or by looking at a specification for the function.

\vskip 6pt
One way to defend against our uncertainty about equivalence classes is to combine combinatorial test generation with random testing. For each argument, partition the space of values into equivalence classes. Then generate test cases, but use the values in those test cases to select randomly from the partitions. This is one way to introduce bias, and control, into random test selection. It points to treating test case generation as a continuum of techniques.

\vskip 6pt
The argument values in test cases could also represent, for instance, the number of times to call a function on an \textsc{api}. The argument values could represent choices about what arguments to pass to each function in a series of function calls.

\vskip 6pt
There are cases where a function has one argument that is a flag and, when it's chosen, other argument values don't make sense to choose. We want to forbid these from the possible input choices. For instance, if \verb|arg1| can be \verb|true| or \verb|false|, and \verb|arg2| can be \verb|default|, \verb|high|, or \verb|low|, but we want to exclude the combination of \verb|false| and \verb|high| or \verb|low|, then the possible outcomes are \verb|true|-\verb|default|, \verb|true|-\verb|high|, \verb|true|-\verb|low|, \verb|false|-\verb|default|. We can either teach the test generator to forbid two combinations, or we can modify the input values, so that \verb|arg12| represents the four possible cases for \verb|arg1| and \verb|arg2| together.

>>>>

While you may already know how to use test case generation from the snippet in the introduction, it can help to think of automated test case generation as a set of steps, each of which has choices to make.
\begin{enumerate}
   \item Identify the system under test.
   \item Decide how a single test case, consisting of argument values, should correspond to a unit test.
   \item Address the risk associated with different arguments.
   \item Pick a test generation strategy.
   \item Choose a method for checking the results of each test.
\end{enumerate}
We'll explore these steps in this section.

@@

We have assumed, thus far, that we are unit testing a function. In that case, the function has arguments and those arguments can take on particular values. Our test cases will correspond exactly to an invocation of the function. However, this need not be the case.

\begin{unnumlist}
\item Integration test of modules, where a module \textsc{api} produces many possible ways to call it.
\item User-level tests of an application, where there are choices in dialog boxes, parameter files, and command-line options.
\item Systems outside of Julia, such as the problem of hardware integration.
\end{unnumlist}

@@

\subsubsection{What arguments represent}
There are two choices to make about arguments and their values. We must decide what the arguments represent and must select particular values for those arguments.

\vskip 6pt
It's rare that a function expects arguments that really take only four possible values. We use integers, floating-point, and strings, but a function argument can be any struct. When we specify tests for \cit, and we choose a few argument values, they are representatives of equivalence classes.

\vskip 6pt
An \emph{equivalence class} is a set of input values that would discover the same faults in the code. For instance, if a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults. Our goal, as authors of unit tests, is to select argument values that represent equivalence classes for the function under test. There isn't a lot of guidance on how to choose these values. You can guess them by looking at the code or by looking at a specification for the function.

\vskip 6pt
One way to defend against our uncertainty about equivalence classes is to combine combinatorial test generation with random testing. Decide that each argument value represents an equivalence class. Then generate test cases, but use the values in those test cases to sample randomly from the partitions. This is one way to introduce bias, and control, into random test selection. It points to treating test case generation as a continuum of techniques.

\vskip 6pt
There are other creative ways to apply automatic test case generation. For instance, if an application reads a \textsc{csv} file, we can use \cit to ensure rows of that \textsc{csv} have a wide mixture of column values. This would improve branch coverage in code that reads the \textsc{csv} as a data frame. Similarly, for module-level testing, arguments could represent choices about calls to a module's functions. Here, consecutive arguments become function calls that are consecutive in time.

\subsubsection{Controlling value choices}

There are cases where a function has one argument that is a flag and, when it's chosen, other argument values don't make sense to choose. We want to forbid these from the possible input choices. For instance, if \verb|arg1| can be \verb|true| or \verb|false|, and \verb|arg2| can be \verb|default|, \verb|high|, or \verb|low|, but we want to exclude the combination of \verb|false| and \verb|high| or \verb|low|, then the possible outcomes are \verb|true|-\verb|default|, \verb|true|-\verb|high|, \verb|true|-\verb|low|, \verb|false|-\verb|default|. We can either teach the test generator to forbid two combinations, or we can modify the input values, so that \verb|arg12| represents the four possible cases for \verb|arg1| and \verb|arg2| together.
